### 2016-04-30 paper.tex
Added geocoding files

\documentclass[12pt,twoside]{article}
\usepackage{problemset}
\usepackage{hanging}
\runningheads{Preston Mui}{Econ-210a: How much did Railroads Affect Market Integration? Evidence from 19th Century France}

@@

@@

\newpage
\begin{thebibliography}{9}

\bibitem{lamport94}
  Leslie Lamport,
  \emph{\LaTeX: a document preparation system},
  Addison Wesley, Massachusetts,
  2nd edition,
  1994.

\end{thebibliography}

>>>>

\documentclass[12pt,twoside]{article}
\usepackage{problemset}
\usepackage{hanging}
\runningheads{Preston Mui}{Econ-210a: Did Railroads Integrate Markets? Evidence from 19th Century France}

@@

Denoting $p_t = (p_{1t},\cdots,p_{Nt})^{\prime}$ as the vector of logged grain prices at $N$ communes at time $t$. Considering a VAR with $L$ lags:
\begin{align*}
	p_t &= v + \sum_{l=1}^L A_l y_{t-l} + \epsilon_t
\end{align*}
This model can be rewritten in the form of a vector error-correction model:
\begin{align*}
	\Delta p_t &= v + \Pi p_{t-1} + \sum_{l=1}^{L-1} \Gamma_l \Delta y_{t-l}  + \epsilon_t
\end{align*}

@@
